Creating the ``r params$package_name`` R package

### 2025-08-23 create-FSHybridPLS.Rmd
proof start

```{r eval=FALSE, include=FALSE}
#' @export
fit.hybridPLS <- function(W, y, n_iter, lambda) {
  # 1. Initialize storage
  W_now <- rho <- xi <- delta <- nu  <- sigma <- eta <- list()

@@

>>>>

```{r eval=FALSE, include=FALSE}
#' @export
fit.hybridPLS <- function(W, y, n_iter, lambda) {
  # 1. Initialize storage
  W_now <- rho <- xi <- delta <- nu  <- iota <- beta <- list()

  # 3. Initialize residuals
  W_now[[1]] <- W
  y_now <- y
  for (l in 1:n_iter) {
    cat(paste(l, "th component", "\n"))

@@

    iota[[l]] <- xi[[l]]
    if (l == 1) {
      beta[[l]] <- scalar_mul.predictor_hybrid( iota[[l]], nu[[l]] )
    } else {
      for (u in 1:(l - 1)) iota[[l]] <- subtr.predictor_hybrid( iota[[l]], iota[[u]], inprod.predictor_hybrid(delta[[u]], xi[[l]]))
      beta[[l]] <- add.predictor_hybrid(beta[[l - 1]], iota[[l]], nu[[l]])
    }
  }
  return (list(
    rho = rho,
    xi = xi,
    W = W_now,
    beta = beta
  ))
}
